Competing Bandits: \\ The Perils of Exploration under Competition

### 2019-02-14 paper/content/barriers.tex
update section labels and fixup appendix
Removed an old color-edit macro.

\section{Data as a Barrier to Entry}\label{section:6}

@@

\asdelete{We explore what factors drive the large market share for the incumbent in the temporary monopoly model.}

Under temporary monopoly, the incumbent can explore without incurring immediate reputational costs, and build up a high reputation before the entrant appears. Thus, the early entry gives the incumbent both a \textit{data} advantage and a \textit{reputational} advantage over the entrant. \asedit{We explore which of the two factors is more significant.}  Our findings provide a quantitative insight into the role of the classic ``first mover advantage" phenomenon in the digital economy.

>>>>

\section{Data as a Barrier to Entry}\label{sec:barriers}

@@

%We explore what factors drive the large market share for the incumbent in the temporary monopoly model.

Under temporary monopoly, the incumbent can explore without incurring immediate reputational costs, and build up a high reputation before the entrant appears. Thus, the early entry gives the incumbent both a \textit{data} advantage and a \textit{reputational} advantage over the entrant. We explore which of the two factors is more significant.  Our findings provide a quantitative insight into the role of the classic ``first mover advantage" phenomenon in the digital economy.
